---
title: "MixedEffectModels"
author: "Susanne Kortsch"
date: "2 3 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Data exploration

Analyses in this document explore the vis_data set generated by the Netlogo model


```{r data setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#data 

setwd("C:/LocalData/susakort/pollinatorsNL-main_18/R_scripts") #set wd to your own directory

vis_data<-readRDS("../Data_output/vis_data.rds") #change to your own local path

```

The vis_data file contains the following information:

**Input**:  

- "../Data_output/vis_data.rds": this data file contains the interaction-wise results per simulation (n=1000).

Our input variables are:  
- run: simulation run number  
- seed_percent: seed percentage (varies between 0.00001 and 1) which determines the habitat heterogeneity. Low seed percentage (<0.001) means the habitats are larger and more homogeneous, whereas higher seed percentages (>0.1) mean that habitats are smaller and the landscape is more heterogeneous.  
- plant.pref: niche and niche preferences (vary between 3.50209e-05 and 1). Graphs cannot be unconnected which means networks always consist of 8 pollinators and 6 plants. the niche and niche preferences result in different network structures (e.g., binary and weighted connectance and nestedness etc).   
- pol.bm: body mass (varies between 1 and 8). These values are taken from an empirical data set (Liam et al.)    
- pl.dens: plant density of a plant within its habitatplant density can vary between 0.1 and 0.9.    
- po.soc: sociality category. 0 is solitary no nest, 1 solitray nest, 2 primitively euscoial, 3 highly eusocial   
- conn: binary connectance of input network    
- nest: binary nestedness of unput network  

**Output**:  

Our response (dependent) variables are:   
- Number_visits=visitation rate   
- cons=consecutive visits  
- pvis=expected pollination visits. These are expected pollination visits are based on the geometric decay assumption (with a 30% decline in pollination probability per visit along a visitation sequence)  
- prefs_after_vis: preferences after the simulation based on the visitation rate  

-wconn.vis: weighted connectance based on visitation rate after the simulation (realised network)  
-wconn.con: weighted connectance based on consecutive visits after the simulation (realised network)  
-wconn.pvis: weighted connectance based on geometric decay visits after the simulation (realised network)  





